Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-06-25 latex/ms.tex
write 2nd para in 2.2, #6

To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample. In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled. Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively. For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled. Assuming invasive sampling, sampled parents in the population 1 are never sampled in the population 2. It should be noted that al the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$ and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation, as explained later.

 The numbers of MS and MO pairs are determined by pairwise comparison of all the sample individuals (${}_{n_{\rm O}}\mathrm{C}_2$ and $n_{\rm M}n_{\rm O}$ comparisons, respectively). As depicted in {\bf Fig~\ref{example}}, six offspring and three mothers are sampled and two MS and three MO pairs are observed. In our modeling framework, if an MS pair also shares a paternal-sibling (PS) relationship, we count it as an MS pair and ignore the existing full-sibling (FS) relationship.

>>>>

To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample. In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled. Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively. For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled. It should be noted that al the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$ and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation. In this section, we only focus HS pairs and PO pairs found between the two populations. For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.

The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}n_{\rm O,2}$ and $n_{\rm O,1}n_{\rm P,2}$ comparisons, respectively). As depicted in {\bf Fig~\ref{cartoon}}, X offspring and Y parents are sampled in the population 1 and X offspring and Y parents are sampled in the population 1, and X HS and Y PO pairs found between the two populations are observed. In addition, X and Y PO pairs found within the same population are observed, which are available to estimate parent numbers, as explain the next section. In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs.
